\subsection{Political Goals for Version 2}

\subsubsection{Subsequent Exploitation}

Incremental economic rights duration is accompanied by a reform of the length of economic rights duration itself and the starting point of its expiration. Unlike the TRIPS treaty this reform uncouples economic rights duration from the authors life time. This however leads to the situation, that a commercial exploitation during the life time of the author is possible without the author benefiting from it. This might lead to a deincentivation of the author which is contrary to the copyright's goal.

The most important point in short duration of economic rights is to give the work back into public domain (at least partially). This mainly means the author (resp. other holder of the economic rights) should not be allowed to exclude anyone from using his work anymore. Note that since private use is already granted, we talk about commercial use here. Between the expiration of the economic rights and the death of the author, we put the work into the state of subsequent exploitation. In this time period nobody needs to ask the author's permission to use the work in a commercial context anymore but is obliged to give a share of his revenue to the author. This share should be relatively small, so that the economic possibilities to use the work are considerably better than during the economic rights duration. A public authority should be entitled to define this minimum share. Collection of these shares could for example be handled by a collecting society.

\subsubsection{Publicly Funded Works}

A special case for the copyright are publicly funded works. These include for example scientific works from a publicly funded universe, maps created by local governments or TV productions of public broadcasting organizations. These works do not need incentivation by copyright. Furthermore, using copyright (especially economic rights) to obstruct the access to these works without reason is not only generally ethically questionable, but also cheating to public that funded it. For that reason we want to liberalize the use of publicly funded works completely, which means to except these works from economic rights.

For this purpose we need a good definition for publicly funded works. Some works might get subsidies from government agencies, but should not count as publicly funded works. Common sense suggests, that at least 50\% of the funding should come from the public. Furthermore since some public employees might try to circumvent this rule (e.g. a professor writing a text book and than publishing it privately) we want to especially include all works, which are created during the working hours and which are covered by the job description of public employees.

\subsection{Code Modifications for Version 2}

\subsubsection{Subsequent Exploitation}

The idea is implemented in the new Art.~\refParagraphN{Par:SubsequentExploitation}.

\subsubsection{Publicly Funded Works}

One option to implement publicly funded works into the code is using the article about claiming economic rights (here: Art.~\refParagraphN{Par:ClaimingAndDurationOfEconomicRights}). Since we introduced that into the code in Version~1, all exceptions could be listed there. For the purpose of overview, we use the new Art.~\refParagraphN{Par:WorksExcludedFromClaimingOfEconomicRights}, which is based on the pattern of Art.~\refParagraphN{Par:ExcludedWorks}.